%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[11pt,a4paper,roman]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
% if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.8]{geometry}
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

\usepackage{import}

% personal data
\name{Rahul}{Ranjan}
% \title{Curriculum Vitae}                               % optional, remove / comment the line if not wanted
\address{IIIT Senapati, \newline Mantripukhri, Imphal (Manipur) 795002 }{}{}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
% \phone[mobile]{909-839-3097}                   % optional, remove / comment the line if not wanted
% \phone[fixed]{01234 123456}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
% \email{xpan1@swarthmore.edu}                               % optional, remove / comment the line if not wanted
% \homepage{shawnpan.me}                         % optional, remove / comment the line if not wanted
% \extrainfo{}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
  
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular} \\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2}
  \end{tabular}
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     {\itshape #3}
  \end{tabular}
  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c c }
\faGlobe\enspace \href{http://rahulranjan.eu5.org/}{Website} &
  \faEnvelopeO\enspace rahul@iiitmanipur.ac.in & \faGithub\enspace \href{https://github.com/imrrahul}{Github} &  \faMobile\enspace (+91)-7301195754\\  
\end{tabular}
\end{center}

\section{ABOUT}
As a Computer Science Under-Graduate with experience in Computer Programming (coding) and
familier with wide range of IT Applications \& Softwares and has a keen interest in Machine Learning
and Artificial Intelligence. As an initiator and task oriented team worker seeking for a position/an internship in a
good and recognised Organisation to develop and enhance my skills.

\section{INTERESTS}
Machine Learning, Artificial Intelligence, Natural Language Processing, Image Processing, Android \& Web Development .

\section{PUBLICATIONS}
\textbf{[1] Finding out the needy one from Tweets : An analysis using \#kerelafloods}\newline
\textbf{Rahul Ranjan}, Himangshu Sarma, Navanath Saharia \newline
Presented the Paper in $3^{rd}$ International Conference on Contemporary Computing and Infor-
matics (Gurgaon, India), 2018 - IEEE Delhi Section.
\newline
\textbf{[2] A speech-based driver assisting module for Intelligent Transport System}\newline
\textbf{Rahul Ranjan}, Himangshu Sarma, Navanath Saharia \newline
Presented the Paper in $3^{rd}$ International Conference on Contemporary Computing and Infor-
matics (Gurgaon, India), 2018 - IEEE Delhi Section.


\section{RESEARCH PROJECTS}


{\customcvproject{A Machine Learning approach for predicting Coronary Heart Disease (CHD) using Risk Factors
}{January 2019 - Present [\textbf{IIITS}]} 
  {\begin{itemize}
    \item Various risk factors which are responsible for heart diseases such as age, sex, height, weight, heart rate, diabetic level, cholestrol level, etc used in predicting the CHD.
    \item The dataset for the project is taken from the UCI Machine Learning Repository https://archive.ics.uci.edu/ml/machine-learning-databases/arrhythmia/
\item The System is trained on the dataset by applying classifiers such as Logistic regression, SVM, etc. to predict other types of CHD (such as Tachycardia, Bradycardia and Coronary artery diseases using ECG signals) to make it more efficient.\end{itemize}
  }
}

{\customcvproject{Building and Using Comparable Corpora for Machine Translation}{Summer 2018 [\textbf{IIT BHU}]} 
  {\begin{itemize}
    \item Used Machine Learning algorithms for finding the solutions the problem.
    \item To make a Parallel Corpus from a Comparable Corpus obtained from wikipedia
dumps for Hungarian- English Language.
\item Used SVM, Logistic Regression
and Random Forest Classifier  on the training and testing data to achieve an accurate of the model.
  \end{itemize}
  }
}


{\customcvproject{Finding out the needy one from Tweets : An analysis using # kerelafloods}{Autumn 2018 [\textbf{IIITS}]}
{\begin{itemize}
  \item Worked on Identifying relevent words from Tweets to help People during disasters (flood).
  \item Implemented Topic Modelling to analyse the use of the system \& Used K-Means, LDA.
  \itemmade in order to help NGOs, Government agencies to help People in kerala
during this destructive flood situation
\end{itemize}
}



{\customcvproject{Sentiment Analysis for racist/provocative words identification from Tweets}{Winter 2018 [\textbf{IIITS}]}
{\begin{itemize}
  \item Worked on detecting the hate speeche containing Tweets.
  \item Used a pre-labelled data for training and testing the model.
  \item Machine Learning algorithms were used (SVM, Logistic Regression) to obtain an accurate system.
\end{itemize}
}

\section{ACADEMIC PROJECTS}

{\customcvproject{Appointment Management System (Android)}{Spring 2018 [\textbf{IIITS}]}
{\begin{itemize}
  \item The proposed system was built as Android Application which will read the received messages
from android device and extract the date and time or words like tommorow , yesterday,etc.
from messages.
  \item The Application will Store these time and dates in the database and manage appointment
calendar for you.
\end{itemize}
}

{\customcvproject{Library Management System  \& Tnp Website (Web)}{Spring 2018 [\textbf{IIITS}]}
{\begin{itemize}
  \item Built Training and Placement Cell Website of IIIT Senapati.
  \item The Application will Store these time and dates in the database and manage appointment
calendar for you.
\end{itemize}
}
\section{EDUCATION}
{\customcventry{July 2016 - Present}{Bachelor of Technology [$6^{th}$ Sem \textbf{(Junior)}]}{Indian Institute of Information Technology Senapati, Manipur }{Imphal, India}{}{}}

{\customcventry{April 2014 - May 2016}{Senior Secondary School}{G.C.S.S}{Purnia, India}{}{}}
{\customcventry{April 2012 - May 2014}{Secondary School}{India Public School}{Purnia, India}{}{}}
\section{KEY SKILLS}
\textbf{Programming Languages} : Fluent in Python, C++; Familiar with Java \& C, PHP, Java Script.\newline
\textbf{Libraries} : Pytorch, NumPy, TensorFlow, Scikit-Learn.\newline
\textbf{Software Skills} : git, MATLAB, GNU Octave, AutoCAD, LATEX, CMake \newline
\textbf{Web Development} : HTML, CSS, JavaScript, PHP, Django, MySQL, PostgreSQL.
\section{EXPERIENCE \& ROLES}
{\customcventry{  July 2018 - Present}{Open Source Developer}{FOSSASIA -An Open Source Organisation }{H.Q.- Singapore}{}
{\begin{itemize}
  \item A regular \& active contributer at FOSSASIA via Github and Gitlab. 
  \item Contributed in various FOSSASIA projects such as SUSI.AI, phimpme-android, open-event-android,etc.
  \item Attended events of FOSSASIA \& Open-source at several places.
\end{itemize}
}
}
{\customcventry{ May 2018 - July 2018}{Summer Research Intern}{Indian Institute of Technology BHU}{Varanasi, India}{}
{\begin{itemize}
  \item Designed and built the Parallel Corpus from Comparable Corpus for Machine Translation.
  \item The Parallel corpus was built for English-Hungarian language so enhance the use of these languages at large scale.
  \item The project is extended for developing such system for Indic languages.
\end{itemize}
}

}

{\customcventry{ Sept 2018 - Present}{Project Assistant}{Indian Institute of Information Technology Senapati}{Imphal, India}{}
{\begin{itemize}
\item Working as a Project Assistant under Dr. Navanath Saharia , Assistant Professor , IIIT Senapati.
  \item Working on Topic Modelling for data related to disaster realted data.
  \item The project aims at implementation of NLP \& Machine Learning concepts for clustering the disaster related data and their Topic Modelling.
\end{itemize}
}

}


\section{AWARDS AND ACHIEVEMENTS}
\begin{minipage}{\maincolumnwidth}%
	\small{
    	\begin{itemize}
    	\item Winner at FOSSASIA (OpenTechNight) Competition and invited for FOSSASIA Open Tech Summit 2019 at Singapore.
          \item Rated Programmer on Competitive Programming Sites.
          \item Received rewards for contributing to Open-Source Projects.
          \item Selected as Delegate for Harvard Project for Asian \& International Relation in Technology \& Innovation track for the two consecutive events at Kuala Lumpur (Malaysia) and Boston M.A. (USA). 
          \item Received 3 Summer Internship Offers from IITs (in 2018 ) to Work in the field of NLP \& Machine
Learning.
\item Rewarded for developing Assistant Application / Alexa Skills for Google Assistant and Amazon Alexa respectively.
\item Received Certificate of Excellence in C, C++, Linux, Java \& LATEX organised by IIT
Bombay.
		\end{itemize}}%
\end{minipage}%
   \section{HOBBIES \& MORE ABOUT ME}
   \begin{itemize}
       \item Open Source Contribution, Competitive Programming, Editing wikipages, Cricket, Watching Documentries \& Web series.
       \item \url{http://rahulranjan.eu5.org/}
       \item Passport No. - \textbf{M0521674}
   \end{itemize}
  
}
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}
\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}                        % 'publications' is the name of a BibTeX file

% Publications from a BibTeX file using the multibib package
%\section{Publications}
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
